Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-04-19 paper/paper.qmd
update paper.qmd and upload sketches

# Create ggplot
ggplot(data = analysis_data, aes(x = Year, y = fertility_rate_total)) +
geom_line(color = "red") +  # Change to line graph
  labs(x = "Year", y = "Fertility Rate, Total (births per woman)")
```
@fig-2 represents South Asia's fertility rate over the span of 21 years i.e. 2000-2020. The fertility rate is represented as the number of children that would be born to a woman if she were to live to the end of her childbearing years and bear children in accordance with age-specific fertility rates of the specified year. The graph depicts a strictly downward trend in the fertility rate over the past two decades. The fertility rate in year 2000 was 3.5722 children per woman which declined over the period of 21 years to 2.2670 children per woman as of 2020.The figure suggests that females in South Asia are choosing to have lesser and lesser number of children in recent times.There could be various social, cultural, economic and political changes that may have influenced this decline in fertility rate.

\newpage

@@

$$ 
Yij = β0 + β1Xij + εij
$$

where:

@@

\newpage

@@

In summary, this linear model suggests a statistically significant negative relationship between female literacy rate and fertility rate which means as female literacy rate increases, the fertility rate will decrease. However, the intercept is not statistically significant. While the model has a high R-squared value, indicating a strong fit to the data, the practical significance of the intercept may be questionable.

# Discussion 
\newpage
# References

>>>>

# Create ggplot
ggplot(data = analysis_data, aes(x = Year, y = fertility_rate_total)) +
geom_line(color = "red") +  # Change to line graph
  labs(x = "Year", y = "Fertility Rate, Total (births per woman)")
```
@fig-2 represents South Asia's fertility rate over the span of 21 years i.e. 2000-2020. The fertility rate is represented as the number of children that would be born to a woman if she were to live to the end of her childbearing years and bear children in accordance with age-specific fertility rates of the specified year. The graph depicts a strictly downward trend in the fertility rate over the past two decades. The fertility rate in year 2000 was 3.5722 children per woman which declined over the period of 21 years to 2.2670 children per woman as of 2020.The figure suggests that females in South Asia are choosing to have lesser and lesser number of children in recent times.There could be various social, cultural, economic and political changes that may have influenced this decline in fertility rate.
\newpage

@@

$$ 
Yij = β0 + β1Xij + εij
$$
where:

@@

@@

The linear regression model suggests a statistically significant negative relationship between female literacy rate and fertility rate which means as female literacy rate increases, the fertility rate will decrease. However, the intercept is not statistically significant. While the model has a high R-squared value, indicating a strong fit to the data, the practical significance of the intercept may be questionable.

# Discussion

## Growth in Female Literacy Rate in South Asia

As analyzed in @fig-1,  the female literacy rate in South Asia is on the rise over the last two decades with a literacy rate of approximately 44.9 percent in the year 2000 to approximately 64.6 percent in 2020. This upward trend is not confined to the past two decades only. South Asia has made a tremendous progress in female literacy rate which was only 21.27 percent in 1975[@The_World_Bank_2024b].

## Declining Fertility Rate (total births per woman)in South Asia

As analyzed in @fig-2,  the fertility rate in South Asia is on the decline over the last two decades with a fertility rate of approximately 3.57 births per woman in the year 2000 to approximately 2.26 births per woman in 2020. This downward trend is not confined to the past two decades only. Fertility rate in South Asia has long been on a decline. The South Asian fertility rate was as high as 6.07 births per woman in 1960[@The_World_Bank_2024c].

## Impact of Female Literacy Rate on Fertility Rate

\newpage
# References
